\documentclass{article}
\usepackage{ShumanNotes}
\title{Homework 2: Materials and Devices}
\author{Kevin Stine}
\date{Due October 11th at 3 PM, 2012}
\setlength{\parindent}{0pt}
\pdfpagewidth 8.5in
\pdfpageheight 11in

\begin{document}
\maketitle

\section{Resistor Color Codes}
\emph{A resistor has the color stripes of red black red gold. What range of resistances could this represent?}
\newline
Modify this line to represent the correct equation for changing the color code to resistance:\newline
Equation:  $color*10+color*10^{color} = resistance$\newline
Modified Equation:  ($color*10+color)*10^{color} = resistance$

\section{OSU Solar Vehicle Team}
\emph{Research the OSU Solar Vehicle Team.}  \newline
Group Website:  \url{http://people.oregonstate.edu/groups/solar/}  \newline
Video:  \url{http://www.youtube.com/watch?v=8jwVyBbDfjY}\newline
Summarize your research and list 2 quetions that you would like answered.\newline
\newline
The OSU Solar Vehicle Team is comprised of five different groups, each focusing on a particular aspect of the vehicle. The mechanical group is in charge of creating the framework for the vehicle, while the body group works on the outer shell of the car. The other three groups are solar cell, electrical, and buisness. The solar cell group is in charge of cutting, soldering, and laminating the solar panels, while the electrical group designs and builds the computer systems for the vehicle. Lastly is the buisness team which is in charge of raising money through advertising. The car itself utilizes 576 solar cells which are each 17.4\% effecient. The frame of the vehicle is made from titanium tubing in an effort to keep the weight down while supporting the suspension.     
\newline
\newline
\begin{enumerate}
\item  Is it possible to make the solar cells more effecient so the car could store more energy and be able to harvest and utilize the energy to its full potential?
\item  Is there another design for the car which could utilize the technology of the solar cells while being a car that has the potential for everyday useage? 
\end{enumerate}

\cfoot{ECE 111 Homework \#2}

\end{document}
